Algorithms for Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2014-10-17 paper/paper.tex
updated table and references

Our work is related to the strategies for deadline-con\-strained
cost-minimization workflow scheduling, developed for utility grid and cloud
systems. However, our problem is different from
\cite{Yu2005},\cite{Abrishami2013158} and~\cite{Young2013} in that we consider
ensembles of workflows instead of individual workflows.
Our work is also different from cloud-targeted autoscaling
solution~\cite{Mao2011} in that we consider ensembles of workflows rather than
unpredictable workloads containing workflows. We also consider budget
constraints rather than cost minimization as a goal. In other words, we assume
that there is more work to be done than the available budget, so some work must
be rejected.
Therefore, cost is not something we optimize (i.e. an objective), but rather a
constraint.

This work is related to bi-criteria scheduling and multi-criteria scheduling of
workflows~\cite{Wieczorek2009,Prodan2010,Dongarra2007,Durillo2013}. These approaches are
similar to ours in that we have two scheduling criteria: cost and makespan. The
challenge in multi-criteria scheduling is to derive an objective function that
takes into account all of the criteria. In our case one objective (amount
of work completed) is subject to optimization, whereas time and cost are
treated as constraints, which is not addressed by other works.

@@

Other approaches for scheduling workflows on grids and clouds such as ~\cite{Talukder2009,Pandey2010} use
metaheuristics that usually run for a long time before producing good results,
which makes them less useful in the scenarios we consider in this paper.

>>>>

Our work is related to the strategies for deadline-con\-strained
cost-minimization workflow scheduling, developed for utility grid and cloud
systems. However, our problem is different from
\cite{Yu2005},\cite{Abrishami2013158} and~\cite{Lee2013} in that we consider
ensembles of workflows instead of individual workflows.
Our work is also different from cloud-targeted autoscaling
solution~\cite{Mao2011} in that we consider ensembles of workflows rather than
unpredictable workloads containing workflows. We also consider budget
constraints rather than cost minimization as a goal. In other words, we assume
that there is more work to be done than the available budget, so some work must
be rejected.
Therefore, cost is not something we optimize (i.e. an objective), but rather a
constraint.
In~\cite{Arabnejad2014} authors introduced a novel single DAG static scheduling PEFT algorithm, 
which outperforms well-known list-based heuristics for makespan optimization, but the budget is not taken into account.

This work is related to bi-criteria scheduling and multi-criteria scheduling of
workflows~\cite{Wieczorek2009,Prodan2010,Dongarra2007,Durillo2013,Durillo2012}. These approaches are
similar to ours in that we have two scheduling criteria: cost and makespan. The
challenge in multi-criteria scheduling is to derive an objective function that
takes into account all of the criteria. In our case one objective (amount
of work completed) is subject to optimization, whereas time and cost are
treated as constraints, which is not addressed by other works.

@@

Other approaches for scheduling workflows on grids and clouds such as ~\cite{Talukder2009,Pandey2010,Durillo2014} use
metaheuristics that usually run for a long time before producing good results,
which makes them less useful in the scenarios we consider in this paper.
